|

### 2022-08-26 appendix/appendix.Rmd
small updates

---
title: |
       | Supplemental Materials for "Legislature Size and Welfare: Evidence from Brazil"
author:
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

@@

\begin{itemize}
\item \textbf{Number of Seats 2000}: Number of city councilors in 2000 (source: TSE).
\item \textbf{Population 2000}: City population according to the 2000 Brazilian Census (source: IBGE).
\item \textbf{Per Capita GDP 2000 (Millions)}: Municipal per capita GDP measured by the Brazilian Census (source: IPEA).
\item \textbf{Proportion of Poverty 2000}: Percentage of citizens earning less than R\$ 70.00 per month (source: Social Development Ministry [MDS]).
\item \textbf{Number of Seats 2004}: Number of city councilors in 2004 according to the Electoral Court (source: TSE).
\item \textbf{Infant Mortality 2005--2008}: Number of children who died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
\item \textbf{Postneonatal Mortality 2005--2008}: Number of children alive for at least 28 days who died before reaching one year of age, divided by the total number of children who lived for 28 days, multiplied by 1,000 (source: DataSUS)
\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
\item \textbf{Quality of Elementary School 2005--2008}: Average municipal IDEB scores. IDEB scores are estimated as follows. The Ministry of Education takes the average of the students' grades in math and Portuguese, then multiply the those numbers by the student yearly approval rate. INEP reweights the estimators to avoid school and classroom specific distortions (source: INEP, years: 2005, 2007).
\item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration who were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
\item \textbf{Number of Females Elected 2004}: Number of females elected to the city council (source: TSE)
\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council. We collect these data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the size of the city council (source: TSE)
\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
\end{itemize}

@@

\begin{table}[htb!]
\centering
\caption{Summary Statistics}
\label{tab:descrvarspaper}
\resizebox{\textwidth}{3in}{
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{\fill}}l r r r r r }
\toprule
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\
\midrule
& \multicolumn{5}{c}{\textbf{Municipal Characteristics}} \\ \cline{2-6}
Number of Seats 2000 & 5,521 & 10.76 & 2.70 & 9 & 21 \\
Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\
GDP Census 2000 & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\
Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\
Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\
& \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
Infant Mortality 2005-2008 & 13,328 & 20.64 & 13.45 & 1.28 & 209.30 \\
Postneonatal Mortality 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
& \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\
Quality of Elementary School 2005-2008 & 9,266 & 3.73 & 0.94 & 0.70 & 8.10 \\
& \multicolumn{5}{c}{\textbf{Bargaining, Coalition, and Public Employment}} \\ \cline{2-6}
Mayoral Pre-electoral coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\
Number of Appointed Bureaucrats 2005-2008 & 16,563 & 67.77 & 126.68 & 0 & 2,894 \\
& \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
Number Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0 & 8 \\
Number Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0 & 9 \\
Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\
Proportion Approved Legislation 2005 & 3,693 & 0.83 & 0.28 & 0.00 & 1.00 \\
& \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
Legislation -- Public Goods & 346,553 & 0.76 & 0.43 & 0 & 1 \\
Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\
Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\
Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\
& \multicolumn{5}{c}{\textbf{Survey -- Strategy to Consolidate Coalition Support}} \\ \cline{2-6}
Coalition Support -- Councilors Job Appointments & 174 & 0.64 & 0.48 & 0 & 1 \\
Coalition Support -- Councilors Demands & 174 & 0.44 & 0.50 & 0 & 1 \\
Coalition Support -- Councilors Personal Requests & 174 & 0.56 & 0.50 & 0 & 1 \\
Coalition Support -- Councilors Legislation & 174 & 0.25 & 0.43 & 0 & 1 \\
Coalition Support -- Councilors Constructions & 174 & 0.43 & 0.50 & 0 & 1 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\textbf{Notes:} The legislation approved dataset contains information on 63 of the 202 municipalities which are 10 thousand inhabitants away from the council size thresholds. Survey summary statistics are unweighted. Numbers of cases vary due to missingness.
\end{tablenotes}
\end{threeparttable}
}
\end{table}

@@

\begin{table}[!htbp] \centering
\caption{Political Effects of Legislature Size -- Placebo Cutoffs}
\label{placresmechreg1}
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l R R R R }
\toprule
 & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections}} \\ \cline{2-5}
& \multicolumn{2}{c}{\textbf{Representation}} &
\multicolumn{2}{c}{\textbf{Elections \& Leg. Productivity}}\\ \cline{2-3}\cline{4-5}
 & \multicolumn{1}{c}{\small{Num. Female}} &
 \multicolumn{1}{c}{\small{Num. Non-white}} &
  \multicolumn{1}{c}{\small{Candidates}} &
  \multicolumn{1}{c}{\small{Prop. Laws}} \\
   & \multicolumn{1}{c}{\small{Councilors}} &
 \multicolumn{1}{c}{\small{Councilors}} &
  \multicolumn{1}{c}{\small{Per Seat}} &
  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.65$^{**}$ &  & -0.72 & -0.001 \\
  & (0.27) &  & (0.48) & (0.06) \\
 N Left & 4620 &  & 4621 & 2990 \\
N Right & 906 &  & 906 & 703 \\
Eff N Left & 414 &  & 567 & 356 \\
Eff N Right & 298 &  & 347 & 229 \\
BW Loc Poly & 4.874 &  & 6.104 & 5.583 \\
BW Bias & 8.789 &  & 10.312 & 8.89 \\
\midrule
 & \multicolumn{4}{c}{\textbf{Panel B: Bargaining, Coalition, and Public Employment}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{Mayoral}} &
 \multicolumn{1}{c}{\small{Num. Politically}} &
 & \\
 & \multicolumn{1}{c}{\small{Coalition Size}} &
 \multicolumn{1}{c}{\small{Bureaucrats}} &  & \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.13 & -0.58 & & \\
  & (0.33) & (17.14)  & & \\
 N Left & 4618 & 13854  & & \\
N Right & 904 & 2709  & & \\
Eff N Left & 654 & 1345  & & \\
Eff N Right & 394 & 915  & & \\
BW Loc Poly & 6.813 & 5.127  & & \\
BW Bias & 10.501 & 8.194  & & \\
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

## Mayor's Characteristics, Revenues, and Transfers from the Central Government

@@

\begin{table}[!htbp] \centering
\caption{Mayor Characteristics}
\label{appmaychar}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
  \hline \\[-1.8ex]
  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\
  & (0.08) & (0.13) & (0.10) & (0.14) \\
  N Left & 5069 & 5069 & 5184 & 5183 \\
  N Right & 335 & 335 & 343 & 343 \\
  Eff N Left & 299 & 226 & 192 & 231 \\
  Eff N Right & 184 & 154 & 141 & 159 \\
  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\
  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

@@

\begin{table}[!htbp] \centering
\caption{Transfers and Revenue}
\label{apptrev}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\
  \hline \\[-1.8ex]
  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\
  & (0.04) & (0.03) & (0.10) & (0.04) \\
  N Left & 15555 & 15555 & 15460 & 14668 \\
  N Right & 1029 & 1029 & 1028 & 998 \\
  Eff N Left & 804 & 258 & 349 & 626 \\
  Eff N Right & 516 & 273 & 333 & 442 \\
  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\
  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

@@

\begin{table}[htb!]
\centering
\caption{Accuracy of SVM Classifier (tested in 20\% of the data)}
\label{accurClassif}
\begin{tabular}{lc}
\hline
\textbf{Variable}            & \textbf{Accuracy}  \\
\hline
Local Public Goods           & 93.8               \\
Oversight                    & 94.9               \\
Education and Health Care    & 92.5               \\
Others                       & 93.5               \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
Age lower than 39         & 0.50         & 0.34       & 0.34           \\
Female            & 0.18         & 0.12       & 0.12           \\
Number of Seats = 9            & 0.83         & 0.90       & 0.90           \\
Number of Seats = 10           & 0.10         & 0.06       & 0.06           \\
Number of Seats = 11           & 0.01         & 0.02       & 0.01           \\
Number of Seats = 12           & 0.01         & 0.01       & 0.01           \\
Number of Seats = 13           & 0.006        & 0.005      & 0.005          \\
Number of Seats = 14           & 0.01         & 0.004      & 0.005          \\
Number of Seats = 15 or more          & 0.02         & 0.009      & 0.008          \\
Region = Central-West & 0.11         & 0.08       & 0.08           \\
Region = Northeast     & 0.33         & 0.32       & 0.32           \\
Region = North        & 0.05         & 0.08       & 0.08           \\
Region = Southeast      & 0.30         & 0.30       & 0.30           \\
Region = South          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}

>>>>

---
title: |
       | Supplemental Materials for "Legislature Size and Welfare: Evidence from Brazil"
author: 
  - Umberto Mignozzetti[^umberto]
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
date: August 26, 2022
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

[^umberto]: Assistant Teaching Professor, Department of Political Science and Computational Social Sciences Program, University of California, San Diego, SSB 393, 2997 Thurgood Marshall Ln, La Jolla, CA 92037, United States of America, <umbertomig@ucsd.edu>, <http://umbertomig.com>. Corresponding author.

[^gabriel]: Associate Professor, Department of Public Policy and International Relations, São Paulo State University, Av. Eufrásia Monteiro Petráglia 900, Franca, SP 14409-160, Brazil, <gabi.cepal@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, Brayford Pool, Lincoln, LN6 7TS, United Kingdom, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.

@@

\begin{itemize}
\item \textbf{Number of Seats 2000}: Number of city councilors in 2000 (source: TSE).
\item \textbf{Population 2000}: City population according to the 2000 Brazilian Census (source: IBGE).
\item \textbf{Per Capita GDP 2000 (Millions)}: Municipal per capita GDP measured by the Brazilian Census (source: IPEA).
\item \textbf{Proportion of Poverty 2000}: Percentage of citizens earning less than R\$ 70.00 per month (source: Social Development Ministry [MDS]).
\item \textbf{Number of Seats 2004}: Number of city councilors in 2004 according to the Electoral Court (source: TSE).
\item \textbf{Infant Mortality 2005--2008}: Number of children who died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS).
\item \textbf{Postneonatal Mortality 2005--2008}: Number of children alive for at least 28 days who died before reaching one year of age, divided by the total number of children who lived for 28 days, multiplied by 1,000 (source: DataSUS).
\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
\item \textbf{Quality of Elementary School 2005--2008}: Average municipal IDEB scores. IDEB scores are estimated as follows. The Ministry of Education takes the average of the students' grades in math and Portuguese, then multiply the those numbers by the student yearly approval rate. INEP reweights the estimators to avoid school and classroom specific distortions (source: INEP, years: 2005, 2007).
\item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE).
\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of municipal bureaucrats of the direct administration who were appointed to jobs (source: IBGE, years: 2005, 2006, and 2008).
\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of municipal bureaucrats of the direct administration hired via admission tests (source: IBGE, years: 2005, 2006, and 2008).
\item \textbf{Number of Councilor Assistants 2005}: Number of city councilor assistants (source: InterLegis).
\item \textbf{Number of Females Elected 2004}: Number of females elected to the city council (source: TSE).
\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council. We collect these data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the size of the city council (source: TSE).
\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis).
\end{itemize}

@@

\begin{table}[htb!]
\centering
\caption{Summary Statistics}
\label{tab:descrvarspaper}
\resizebox{\textwidth}{3in}{
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{\fill}}l r r r r r }
\toprule
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\
\midrule
& \multicolumn{5}{c}{\textbf{Municipal Characteristics}} \\ \cline{2-6}
Number of Seats 2000 & 5,521 & 10.76 & 2.70 & 9 & 21 \\ 
Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\ 
GDP Census 2000 & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
Proportion of Poverty Census 2000 & 32,845 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\
& \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\ 
Postneonatal Mortality 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
& \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
& \multicolumn{5}{c}{\textbf{Bargaining, Coalition, and Public Employment}} \\ \cline{2-6}
Mayoral Pre-electoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0 & 17 \\ 
Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
Num. Career Bureaucrats & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
Num. Councilor Assistants & 5,523 & 4.63 & 8.55 & 0 & 213 \\
& \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
Number Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0 & 8 \\ 
Number Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0 & 9 \\ 
Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\
& \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
Legislation -- Public Goods & 346,553 & 0.76 & 0.43 & 0 & 1 \\ 
Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\ 
Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\
& \multicolumn{5}{c}{\textbf{Survey -- Strategy to Consolidate Coalition Support}} \\ \cline{2-6}
Coalition Support -- Councilors Job Appointments & 174 & 0.64 & 0.48 & 0 & 1 \\ 
Coalition Support -- Councilors Demands & 174 & 0.44 & 0.50 & 0 & 1 \\ 
Coalition Support -- Councilors Personal Requests & 174 & 0.56 & 0.50 & 0 & 1 \\ 
Coalition Support -- Councilors Legislation & 174 & 0.25 & 0.43 & 0 & 1 \\ 
Coalition Support -- Councilors Constructions & 174 & 0.43 & 0.50 & 0 & 1 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\textbf{Notes:} The legislation approved dataset contains information on 63 of the 202 municipalities which are 10 thousand inhabitants away from the council size thresholds. Survey summary statistics are unweighted. Numbers of cases vary due to missingness.
\end{tablenotes}
\end{threeparttable}
}
\end{table}

@@

\begin{table}[!htbp] \centering
\caption{Political Effects of Legislature Size -- Placebo Cutoffs}
\label{placresmechreg1}
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l R R R R }
\toprule
 & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections}} \\ \cline{2-5}
& \multicolumn{2}{c}{\textbf{Representation}} &
\multicolumn{2}{c}{\textbf{Elections \& Leg. Productivity}}\\ \cline{2-3}\cline{4-5}
 & \multicolumn{1}{c}{\small{Num. Female}} &
 \multicolumn{1}{c}{\small{Num. Non-White}} &
  \multicolumn{1}{c}{\small{Candidates}} &
  \multicolumn{1}{c}{\small{Prop. Laws}} \\
   & \multicolumn{1}{c}{\small{Councilors}} &
 \multicolumn{1}{c}{\small{Councilors}} &
  \multicolumn{1}{c}{\small{Per Seat}} &
  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
LATE & 0.65$^{**}$ &  & -0.72 & -0.001 \\ 
  & (0.27) &  & (0.48) & (0.06) \\ 
 N Left & 4620 &  & 4621 & 2991 \\ 
N Right & 906 &  & 906 & 703 \\ 
Eff N Left & 414 &  & 567 & 356 \\ 
Eff N Right & 298 &  & 347 & 229 \\ 
BW Loc Poly & 4.874 &  & 6.104 & 5.585 \\ 
BW Bias & 8.789 &  & 10.312 & 8.893 \\
\midrule
 & \multicolumn{4}{c}{\textbf{Panel B: Bargaining, Coalition, and Public Employment}} \\ \cline{2-5}
 & \multicolumn{1}{c}{\small{Mayoral}} &
 \multicolumn{1}{c}{\small{Num. Politically}} &
 & \\
 & \multicolumn{1}{c}{\small{Coalition Size}} &
 \multicolumn{1}{c}{\small{Bureaucrats}} &  & \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.13 & -0.58 & 92.83 & -2.16 \\ 
  & (0.33) & (17.15) & (63.66) & (1.80) \\ 
 N Left & 4618 & 13855 & 13850 & 4618 \\ 
N Right & 904 & 2709 & 2708 & 905 \\ 
Eff N Left & 654 & 1345 & 2268 & 598 \\ 
Eff N Right & 394 & 915 & 1277 & 364 \\ 
BW Loc Poly & 6.813 & 5.126 & 7.672 & 6.323 \\ 
BW Bias & 10.501 & 8.194 & 13.251 & 11.031 \\
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

## Mayors' Characteristics, Revenues, and Transfers from the Central Government

@@

\begin{table}[!htbp] \centering
\caption{Mayor Characteristics}
\label{appmaychar}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
  \hline \\[-1.8ex]
  LATE & 0.07 & -0.06 & -0.10 & 0.06 \\ 
  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
 N Left & 5069 & 5069 & 5184 & 5183 \\ 
N Right & 335 & 335 & 343 & 343 \\ 
Eff N Left & 300 & 232 & 195 & 233 \\ 
Eff N Right & 184 & 155 & 145 & 159 \\ 
BW Loc Poly & 11.772 & 9.832 & 8.611 & 9.681 \\ 
BW Bias & 17.081 & 15.8 & 13.399 & 14.758 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

@@

\begin{table}[!htbp] \centering
\caption{Transfers and Revenue}
\label{apptrev}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\
  \hline \\[-1.8ex]
  LATE & 0.03 & -0.02 & 0.17$^{*}$ & 0.06 \\ 
  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
 N Left & 15555 & 15555 & 15460 & 14668 \\ 
N Right & 1029 & 1029 & 1028 & 998 \\ 
Eff N Left & 858 & 282 & 409 & 735 \\ 
Eff N Right & 540 & 294 & 357 & 481 \\ 
BW Loc Poly & 11.254 & 4.922 & 6.496 & 10.248 \\ 
BW Bias & 16.599 & 8.382 & 11.603 & 15.583 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

@@

\begin{table}[htb!]
\centering
\caption{Accuracy of SVM Classifier (Tested in 20\% of the Data)}
\label{accurClassif}
\begin{tabular}{lc}
\hline
\textbf{Variable}            & \textbf{Accuracy}  \\
\hline
Local Public Goods           & 93.8               \\
Oversight                    & 94.9               \\
Education and Health Care    & 92.5               \\
Others                       & 93.5               \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[htp!]
\centering
\caption{Proportions for Each Bin Used in the Weighting Process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
Age lower than 39         & 0.50         & 0.34       & 0.34           \\
Female            & 0.18         & 0.12       & 0.12           \\
Number of Seats = 9            & 0.83         & 0.90       & 0.90           \\
Number of Seats = 10           & 0.10         & 0.06       & 0.06           \\
Number of Seats = 11           & 0.01         & 0.02       & 0.01           \\
Number of Seats = 12           & 0.01         & 0.01       & 0.01           \\
Number of Seats = 13           & 0.006        & 0.005      & 0.005          \\
Number of Seats = 14           & 0.01         & 0.004      & 0.005          \\
Number of Seats = 15 or more          & 0.02         & 0.009      & 0.008          \\
Region = Central-West & 0.11         & 0.08       & 0.08           \\
Region = Northeast     & 0.33         & 0.32       & 0.32           \\
Region = North        & 0.05         & 0.08       & 0.08           \\
Region = Southeast      & 0.30         & 0.30       & 0.30           \\
Region = South          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}
